Collision rates of planetesimals near mean-motion resonances

### 2021-01-25 refereeResponse.txt

We appreciate the referee's thorough and careful comments. We will address concerns with the manuscript one by one, with the original comment listed first, followed by our response (indented).

@@

1) It is not clear how collisions were treated. Wallace et al. point to other papers that describe the implementations of the collisional algorithms. Although I agree they should not attempt to describe all details of the code here, it would be of major help to add more text describing how they deal with collisions.

	A more detailed discussion of the collision model has been added to the end of section 3.1. Most importantly, it is now explicitly stated that we only model the planetesimal-planetesimal collisions.

@@

1.1) What is the collisional scaling used?

	All collisions result in perferct mergers (although the subsequent growth of the planetesimals does not matter much, as no bodies in any of the simulations happen to undergo more than a single collision). This is now stated in section 3.1. We do not model the subsequent evolution of any of the debris.

@@

1.2) What material is assumed for the colliding planetesimals?

	A 2 g cm^-3 bulk density corresponds to an even mixture of ice and rock. Because of our simple collision model, this only affects the mass-radius relation of the bodies.

@@

1.3) How do you deal with size frequency distribution (collisional cascade) resultant from collisions?

	We assume that there is a direct correspondence between the local collision rate and the amount of dust present. As the referee points out below, the spatial evolution of bodies between dust and planetesimal sizes might have a significant influence of the final dust distribution. We have made sure to highlight this concern throughout the paper, and provide a somewhat crude calculation in section 5 which suggests that this assumption is not terribly unreasonable.

@@

1.4) What is the dust size considered in this work?

	We assume that the resulting dust grains are 1mm in size. This is mentioned in section 5 (section 4.2 in the original draft).

@@

I would say all these matter a lot once 300 km planetesimals will likely not be instantaneously pulverized to dust-size when they collide. Thus it is of major importance for the understanding of this work, to know precisely how collisions were treated. If, for instance, authors did not consider any fragmentation, and only tracked collisions to determine where dust would form, I would say this should be put as a caveat.

The reason why I'm asking this to be a caveat is because in this case the authors' results would not necessarily be representing the dust profile, but rather the planetesimal collisional profile, and so the upper limit of dust generation at a given location. This makes a difference regarding the applicability of this work, once the expected real signals from the bumps and dips would be much smaller, and so particularly undetectable. The conclusion's by Wallace et al., potentially based on a local upper limit of dust generation, already points towards an expected faint signal in real observation. Therefore, if the real expected signal end up being even fainter, would this work results be applicable at all, or would them be simply negative results? I am afraid that if the results would be simply negative, they may not be important. I mean, why should we care if we will not be able to easily see those bump/dip features? In this case we would not be able to say anything about the mass and eccentricity of the potential perturbing planet. Therefore, what is the meaning of constraining something that it is unmeasurable?

I would try to help the authors and turn this into a positive light, even if the results turn to be negative. One could eventually say that, once observational capabilities improve, having a constrained measurement would help to quickly interpret images in the future. I don't know how likely is this, but with a proper caveat, it would be acceptable, eventually.

	This is an excellent point brought up by the referee and is something that deserves a more careful discussion of in the paper. In regards to the applicability of this work: one must first understand where and how the planetsimals collide if there is any hope of nailing down what the resulting dust distribution will look like. Going from the planetesimal collision profile to a dust emission profile deserves an entire paper by itself and we certainly do not do that analysis justice here.

@@

2) I am very concerned by the fact the authors neglected migration on small particles due to aerodynamic drag. 300 km planetesimals will not break down to dust directly (of course some dust will be created during the 300 km planetesimal's collisions, but that would be a very small fraction of mass). The 300 km planetesimals (depending on material) will more likely break into a collection of smaller km-size objects. These smaller size objects will then overpopulate the regions where they were created, thus enhancing collision rates among them. Collisions that continue to happen among these smaller objets will eventually turn them in to a very large swarm of even smaller m- to km-size objects. Ultimately, this last generation of collisionally evolved planetesimals will become dust (then my question about how and if Wallace et al. considered collisional cascade in their simulations).

The problem of neglecting aerodynamic drag becomes then a bigger problem because, as it is very well known, small m- to km-sized objects feel strong headwind and thus can drift very fast Sunwards (e.g. Weidenschilling & Davis 1985; Patterson 1987; Beauge & Ferraz-Mello 1993; Malhotra 1993; Gomes 1995a,b; Jiang & Yeh 2004; Batigyn & Laughlin 2015; Storch & Batygin 2019; Deienno et al. 2020). Therefore, dust created by these large moving swarms could leave a signature that is far different than that when assuming dust would be generated in the location of the 300 km planetesimal collisions (eventually changing, or even destroying, the bump/dip signatures; despite the fact that dust would couple to the gas almost instantaneously, once created). This is why I previously said authors may be tracking the planetesimal collisional profile and the upper limit of dust generation at those locations in their simulations, but not necessarily the dust profile.

	In the original paper, we checked to ensure that the 300 km planetsimals and the mm-sized (and smaller) dust grains would stay in place, but the referee's concern about the effects of radial drift of intermediate-sized bodies is an important point that was overlooked. We handle this by: 1. cautioning the reader that the dust emission profiles presented should be interpreted as upper limits 2. discussing the concerns brought up by the referee 3. Providing a (somewhat crude) calculation of the drift and collision timescale of 1m bodies, where drift should be maximal. Point 3 is discussed more below.

@@

They should discuss:
2.1) If drift timescale of 1 m- to 1 km-sized objects is larger than their collision timescale.
In this case, collisions would happen before planetesimals would drift. Then the results should hold true.
2.2) If drift timescale of 1 m- to 1 km-sized objects is smaller than their collision timescale.
In this case, planetesimals would tend to drift faster than they can collisionally evolve. However, if their drift timescale is still larger than 5000 yr (integration time), then maybe this could be a minor issue. But a caveat would still be necessary as the large swarm of small planetesimals would likely continue collisionally evolving elsewhere (far from the mean motion resonances; MMRs, thus potentially changing the bump/dip signatures).
2.3) If drift timescale is smaller than 5000 yr and also smaller than collisional timescale.
In this case, this is a major issue! Planetesimals would quickly fall into the star, leaving minor dust signature, or a continue dust signal throughout their migration path, thus certainly no bumps nor dips would be observed.

Regardless the situation, this should be clearly discussed in the text.

	In section 5, we now provide a calculation of both the drift timescale and collision timescale for 1m bodies near the 2:1 MMR. Because we do not model the debris from planetesimal collisions, the collision timescale for the 1m bodies is found by extrapolating the collision rate of the planetesimals down to smaller bodies. This is done in the following way:

		1. Measure the collision rate (per particle) of the planetesimals from the e2m2 simulation inside the 2:1 MMR
		2. Assume that the 1m bodies will have the same dynamical state (eccentricity and inclination dispersion) as the planetesimals
		3. Assume that all of the mass in solids near the 2:1 MMR now consists of 1m bodies
		4. Scale the planetesimal collision rate (measured in the simulation) by the factor by which the number density and collision cross section would change if one were to convert the planetesimal population to smaller bodies. In this way, we get and estimate for the collision timescale for 1m bodies.

	In doing so, we estimate that the collision timescale for 1m bodies is up to 100x-1000x smaller than the drift time for those bodies across the resonance. This suggests that radial drift will not have a large influence on the resulting dust dustribution. However, the 1m collision timescale should be interpreted as an lower limit, due to assumptions 2. and 3 listed above. We conclude that it is *plausible* that radial drift does not play an important role, although a full, proper treatment of the collisional cascade and drift process is necessary to say this with certainty.

@@

Summarizing, if interior MMRs can't capture small drifting planetesimals (or even in the case where capture would eventually occur), aerodynamic drag plus collisional evolution would not leave any object in MMRs. Therefore, the bumps and dips observed in this work would eventually not exist.

Not that I want to sound like a broken record, but in my opinion, without considering small planetesimals drifting due to gas drag, the figures presented in this work represent a planetesimal collisional profile, but not necessarily a dust profile. Again, large amounts of dust will not be directly generated by collisions among 300 km planetesimals, but rather by collisions among a larger swarm of m- to km-sized objects. The latter are strongly affected by the gas and don't strongly interact with interior MMRs, unless the planet in migrating Sunwards and capturing them (not the case of the present work).

    See our response to concern 2). The referee is absolutely correct that the connection we have made between the planetesimal collision profile and the dust profile is rather tenuous.

@@

4) Wallace et al. performed each simulation for 5000 years. In the introduction, authors claim all works to date are severely limited in simulation time. Well, is 5000 years different than that? Deienno et al. (2020) performed N-body simulations of collisionaly evolving planetesimals (using statistical routines and tracer particles) with N of order O^10+ for 100,000 yr! I understand the codes used and the purpose of the two works were very different, so as the simulation setups. However, I don't understand why 5000 yr is not a severely limited time either. Protoplanetary disks can live much longer than that (Myr timescales). Why 400 orbits is enough? Wouldn't a longer simulation time change all results? I mean, the way it is, I understand that the disk signatures would be those reflecting a 5000 yr evolution, which is basically the observational instant considering how long a disk could live. However, if a 10,000 yr or 100,000 yr evolution would change the dust signatures (especially if considering aerodynamic drag), how applicable are the conclusions in this work? See that 10,000 yr or 100,000 yr are also short periods compared to the disk lifetime. Could you, please, add discussion regarding simulation time, as well as, clearly define what is a short and a long time (and why)? For me 5000 yr is, in principle, too short.

	Other studies which directly resolve planetesimal collisions near MMR with N-body methods (Richarson et al 2000, Dobinson 2013) used an integration time that shorter than the libration timescale of the resonances. This is what we mean by 'severely limited'. The text in the introduction has been changed to clarify this.

	Regarding other codes that make use of tracer particles (such as Deienno et al. 2020), one would worry that the phase space resolution may not be sufficient to fully resolve the dynamics that are happening, particularly near the edges of the resonances. It is doubtful that statistical routines would capture this either, unless it was explicitly built in to the code.

	Given that gas drag does not have a significant influence on the planetsimals (and it's plausible that the same is true for the collisional debris), we do not expect that a longer integration time should affect our results. The integration time we have chosen (5,000 years) is longer than any of the relevant timescales relating to the dynamics of the planetsimals. We now present a calculation all of the relevant timescales relating to the dynamics of the planetesimals in section 2. We have also added an expanded discussion justifying our choice of integration time to the beginning of section 4. In addition, section 5 contains a discussion of timescales relating to the debris from the collisional cascade process.

@@

The question of applicability:

If I understood the applicability of this work would follow the steps:
1) Once a bump or dip is observed in the dust emission signature of a disk, one would need to assume that this bump or dip reflects the position of the interior 2:1 MMR with a planet.
2) Thus, one would need to look for another dip or bump near what would be the interior 3:1 MMR with that supposed planet.
3) Only then one would be able to guess on the eccentricity and mass of the assumed perturber.

I think this should be clearly said in the conclusions, as well as this idea should be introduced somewhere upfront in the manuscript (maybe in the abstract or introduction). I would not leave to the reader to reach this conclusion. Readers can easily interpret things wrong (especially nowadays where we have so much things to read and we usually read them fast). Did I have the right interpretation or are the author suggesting something different in regards to applicability?

    This is the correct interpretation. The outline at the end of the introduction now lays this out. In addition, there is a step-by-step description of this process toward the end of section 7 (section 6 in the original draft).

@@

General points (not in order of importance, but as they appear in the text):

I will use the following nomenclature:
- page 2, left(right) column, third paragraph, line 36 as pg.2 l(r)col. P.3 l.36 (line number reflects the number on the left side of a given page and not the paragraph line.)

1) pg.1 lcol P.1 l.47 - "or orbiting externally" - why not considering the planets orbiting internally too? External MMRs are important and can have a much larger effect in debris disk.

    This is absolutely true. The initial conditions for this work are meant to be compared with simulation B of Richardson et al. 2000, which only focused on the internal MMRs. The phrase 'orbiting externally' was changed to 'orbiting adjacent to'. The reason we did not explore exterior MMRs in this work is because doing so is more computationally expensive. (Many more orbits required for collisions to occur)

@@

2) pg.1 lcol P.1 l.49-51 - "In gas-poor/debris systems, a giant planet perturber can also influence the structure of the dust continuum emission." - Why discussing debris disk if you will only account for the gaseous phase? This confuses the reader.

	Although the presence of gas is necessary in order to justify a simple, tractable model for connecting the planetesimal collision profile to the dust profile, the dynamics of the planetesimals and the resulting planetesimal collision profile does not depend very strongly on the gas. In a debris disk, we can't connect the planetesimal collision profile and the dust profile in such a simple way, but the behavior of the planetesimals should be quite similar.

@@

3) pg.1 rcol P.2 l.44-47 - "Dobinson et al. (2013) showed that collisional dust that... to infer the presence of the planet." - In a debris disk or in a gas disk?

    The Dobinson et al. 2013 work modeled the inner, gas-poor region of a transition disk. The term 'planetesimal disk' in our introdution was changed to 'inner part of a transition disk' to make this more clear.

4) pg.2 lcol P.1 l.44-47 - "Unfortunately, collision detection in an N-body simulation is extremely computationally expensive. So far, studies of planetesimal dynamics near MMRs have involved either collisionless test particles (Boley 2017; Tabeshian &Wiegert 2016, 2018) or severely limited integration times (Richardson et al. 2000). To further elucidate this subject, we use the tree based N-body" - But see Deienno et al. (2020).

    Deienno et al. 2020 makes use of tracer particles, which is not the case with the other studies we cite here. Had we used coarser resolution and taken advantage of tracer particles in this work, the structure seen at the edges of the resonances in figures 7 and 8 (figures 6 and 7 in the original paper), which is critical to generating the features seen in the collision profiles, is unlikely to have been resolved. The text in the above sentence in the introduction has been modified to clarify that we are only referring to cases where the planetesimals are directly modeled.

@@

5) A general comment - The introduction is confusing. It is clear from the abstract that the work will consider only the gas disk phase of a protoplanetary disk. However, because the introduction discuss a lot of debris disk, it is not clear whether debris disks will be considered. I would suggest focusing the discussion on protoplanetary disk. This way it would be clear authors will work during the gas phase.

	We have made edits to the abstract, introduction and conclusion to place more emphasis on the behavior of the planetesimals, which should be similar in both a protoplanetary disk and a debris disk. As we show in section 2.4 (newly added), the gas has an incredibly weak effect on the planetesimals and their resulting motion and collisions should be similar in both a gas-rich and gas-poor system.

@@

6) Another general comment, now regarding section 2. - A much more relevant dynamics not discussed at all is due to aerodynamic gas-drag on planetesimals (especially the smaller ones). Also, collision rates are not discussed at all !

   Good point! Two additional subsections have been added to section 2, which discuss both gas drag on planetsimals and collisions between planetesimals.

@@

7) Reference - Murray & Dermott (2000) - I think Murray & Dermott (1999) is a better reference (at least more commonly used).
\bibitem[\protect\citeauthoryear{Murray \& Dermott}{1999}]{1999ssd..book.....M} Murray C.~D., Dermott S.~F., 1999, ssd..book

    Never noticed this before! All Murray & Dermott references have been changed to the 1999 version.

8) pg.2 rcol P.1 l.8-9 - "... along with aerodynamic gas drag will..." - Even at this point is still not clear from the text if gas will be considered. Please, clarify the text.3

    This is now clarified at the end of section 2.4 (gas drag on planetesimals) and in section 3.2 (initial conditions). The idea is that we consider the effects gas drag when building the initial conditions, but do not need directly model it during the course of the simulations because the gas drag and gravitational stirring timescales (which counteract each other) are quite long. We assume that these two effects are in equilibrium, build them into the initial conditions (through the eccentricity and inclination dispersions) and then can safely forget about them.

@@

9) A general comment with respect to section 2.2 - It looks like there are typos in some of the equations. I would also suggest that, every time that equations from other works are quoted, please, say chapter, page, and eq #. This helps the reader to look after, if a bit more of background is needed. Finally, I don't understand the importance of this section. It ends as: "Due to the complicated dynamics that are at play in this region, we turn to a direct N-body treatment to better understand how the collision rate varies in the vicinity of a MMR.". When I reached this point I asked myself: Will this section be used for something or is it here simply to say that the dynamics are complicated enough to be treated analytically, thus needing numerical analysis? I would suggest to shorten this section. Another suggestion, consider moving it to an appendix (once equations are revised).

	Chapter, page number and equation number have now been added alongside all equations pulled from Murray and Dermott. This section has been repurposed a bit, and some of the more detailed parts have been moved to the appendix. The main purpose of this section is now to present calculations for the timescales of dynamical effects (secular forcing, libration in MMR, aerodynamic gas drag) that act on the full-sized planetesimals. Note that all of the discussion and calculations of the dynamics of the collisional debris is saved for section 5. Most of the detailed references to Murray and Dermott have been moved to the appendix, as this is probably an unnecessary amount of detail for the typical reader.

@@

I am not saying equations are wrong, but please, revise all equations to make sure they are correct and consistent, and add explanation when clarification is needed.

10) Equation (5) - should'n this equation have -q instead of -(2p+q) in the third term and -p instead of -q in the second term? See for example Murray & Dermott (1999, chap 8, eq. 8.8), or Beaugé & Ferraz-Mello (1993), or Malhotra (1993), or Gomes (1995)...
From Murray & Dermott (1999, Chap 6 and 8), one of the general forms of the resonant angle can be phi = j1*lamb' + j2*lamb + j4*varpi, where j1 = p+q, j2 = -p and j4 = -q. So why using j2 = -q and j4 = -(2p+q) instead?
The authors should explicitly say, and explain why these choices were made.

    The argument should indeed by -q, rather than -(2p+q). This mistake was carried through when writing up the equations in the paper, although it appears we properly used j4 = -q when doing our analysis and constructing the plots. (2p+q) has been replaced by q in equations 5 and 6 in the original draft (equations 5 and B1 in the revised version).

@@

15) pg.3 lcol P.2 l.28 - "... equation 8.76)." - with j2 = p.

    Added

16) pg.3 lcol P.4 l.34-35 - "The net result of this is that MMRs will produce spikes in the semimajor axis-eccentricity distribution of a planetesimal disc." - This is true when migration due to aerodynamic drag is not considered, or for large planetesimals that don't feel strong headwind. Would this still be true for small planetesimals that are drifting inwards? That would largely depend on the relation strength of the resonance vs drifting timescale (resonance crossing time).

### 2021-01-25 main.tex
Move figures backward in text a little

\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock)} and a diameter of 
300 km. \textbf{This choice of parameters for the planetesimal disk is meant to mimic the setup used in simulation B by \citet{2000Icar..143...45R}. One difference from the aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000. This allows us to use a finer base timestep size, which, as we will discuss in section \ref{sec:results}, appears to be the reason why no features were seen in the collision profile near the resonances by \citet{2000Icar..143...45R}}.

@@

\textbf{We first provide a justification for assumption (1), which is as follows: At 3 AU in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$). This places any dust grains in the Epstein drag regime, with a stopping timescale given by}

@@

\noindent where $\rho$ is the bulk density of the dust grain, $s$ is its size, and $v_{th}$ is the local thermal velocity of the gas. At 3 AU in the protosolar nebula, $v_{th} \sim 10^{5}$ cm s$^{-1}$. Assuming a 1 mm dust grain with a $\rho$ = 2 g cm$^{-3}$, the stopping time is $\sim 10^{-4}$ yr.  This is orders of magnitude smaller than the 
orbital timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.

@@

\textbf{Radial drift is maximized for bodies of the size at which St = $t_{s} \Omega$ = 1. In the Stokes drag regime at 3 AU, this occurs for bodies of 1 meter in size. Following a similar calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years. Although we do not model collisions between bodies of this size, a lower limit on the collision timescale for these objects can be obtained by extrapolating the planetesimal collision rate measured in our simulations down. For the e2m2 simulation, we find that 125 collisions occur within the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr. There are a total of 15,000 planetesimals within this region, which means that a single planetesimal undergoes a collision every $\sim$ 370,000 years on average. If the entire planetesimal population in this region were converted to 1 meter bodies with the same bulk density, the number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$. The collision timescale would therefore decrease to $\sim$ 1 year. As shown above, radial drift in the Stokes drag regime is maximized for bodies of 1 meter in size, which is only a factor of two larger than the mean free path of the gas particles. It is therefore not entirely clear if the Stokes drag law is appropriate here. Because of this, we also repeat the above calculation for bodies that experience Epstein drag. With this assumption, we find that radial drift is maximized for a cm-sized body. If one were to instead convert all of the collisional debris to objects of this size, the collision timescale decreases by another factor of 100. We conclude that the true collision timescale for bodies with maximal radial drift lies somewhere between $10^{-2}$ and 1 year.  From this crude calculation, it appears plausible that the collision timescale for the fastest inward drifting bodies is smaller than their drift timescale across the 2:1 MMR. We argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the physics before additional complexity is later added.}

@@

Compared to using the corotating gap opened by the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring 
variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs\textbf{, so long as the dust profile closely matches the collisional profile of the planetesimals.}. Another complicating factor is that 
the inner $\sim$ 10 au of most protoplanetary discs are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
wavelengths where the inner disc is optically thin. This comes at the expense of much poorer resolution. However, future radio facilities like the NG-
VLA are expected to achieve sub-AU resolution for nearby planet-forming discs \citep{2018ASPC..517..147R}. In the more near-term, techniques 
like Gaussian process fitting present a promising way to recover substructure at sub-beam resolution \citep{2020arXiv200507709J}.

>>>>

\noindent with $\alpha$ = 3/2 and $\Sigma_{0}$ = 10 g cm$^{-2}$. Planetesimals are given a bulk density of 2 g cm$^{-3}$ \textbf{, which corresponds to a mixture of ice and rock,} and \textbf{are given a} diameter of 
300 km. \textbf{This choice of parameters for the planetesimal disk is meant to mimic the setup used in simulation B by \citet{2000Icar..143...45R}. One difference from the aformentioned study is that we use a narrower annulus, which reduces the number of particles required from $10^6$ down to roughly 500,000. This allows us to use a finer base timestep size, which, as we will discuss in section \ref{sec:results}, appears to be the reason why no features were seen in the collision profile near the resonances by \citet{2000Icar..143...45R}}.

@@

\textbf{We first provide a justification for assumption (1), which is as follows: At 3 au in the protosolar nebula, the mean free path of a gas particle is $\sim$ 50 cm (assuming a composition of pure hydrogen with a local volume density of $\rho_{g} = 4 \times 10^{-10}$ g cm$^{-3}$). This places any dust grains in the Epstein drag regime, with a stopping timescale given by}

@@

\noindent where $\rho$ is the bulk density of the dust grain, $s$ is its size, and $v_{th}$ is the local thermal velocity of the gas. At 3 au in the protosolar nebula, $v_{th} \sim 10^{5}$ cm s$^{-1}$. Assuming a 1 mm dust grain with a $\rho$ = 2 g cm$^{-3}$, the stopping time is $\sim 10^{-4}$ yr.  This is orders of magnitude smaller than the 
orbital timescale, therefore we conclude that collisionally generated dust grains will immediately couple to the gas.

@@

\textbf{Radial drift is maximized for bodies of the size at which St = $t_{s} \Omega$ = 1. In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size. Following a similar calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years. Although we do not model collisions between bodies of this size, a lower limit on the collision timescale for these objects can be obtained by extrapolating the planetesimal collision rate measured in our simulations down. For the e2m2 simulation, we find that 125 collisions occur within the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr. There are a total of 15,000 planetesimals within this region, which means that a single planetesimal undergoes a collision every $\sim$ 370,000 years on average. If the entire planetesimal population in this region were converted to 1 meter bodies with the same bulk density, the number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$. The collision timescale would therefore decrease to $\sim$ 1 year. As shown above, radial drift in the Stokes drag regime is maximized for bodies of 1 meter in size, which is only a factor of two larger than the mean free path of the gas particles. It is therefore not entirely clear if the Stokes drag law is appropriate here. Because of this, we also repeat the above calculation for bodies that experience Epstein drag. With this assumption, we find that radial drift is maximized for a cm-sized body. If one were to instead convert all of the collisional debris to objects of this size, the collision timescale decreases by another factor of 100. We conclude that the true collision timescale for bodies with maximal radial drift lies somewhere between $10^{-2}$ and 1 year.  From this crude calculation, it appears plausible that the collision timescale for the fastest inward drifting bodies is smaller than their drift timescale across the 2:1 MMR. We argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the physics before additional complexity is later added.}

@@

Compared to using the corotating gap opened by the planet as a diagnostic \citep{2013ApJ...777L..31D, 2016ApJ...820...29D}, measuring 
variations in the dust emission near MMRs is much more subtle and requires much higher spatial resolution and sensitivity. As we have shown, the 
bump vs dip feature near the 2:1 MMR is marginally detectable with ALMA for the nearest protoplanetary discs\textbf{, so long as the dust profile closely matches the collisional profile of the planetesimals.}. Another complicating factor is that 
the inner $\sim$ 10 au of most protoplanetary discs are optically thick in the sub-mm. The solution to this problem is to instead observe at longer 
wavelengths where the inner disc is optically thin. This comes at the expense of much poorer resolution. However, future radio facilities like the NG-
VLA are expected to achieve sub-au resolution for nearby planet-forming discs \citep{2018ASPC..517..147R}. In the more near-term, techniques 
like Gaussian process fitting present a promising way to recover substructure at sub-beam resolution \citep{2020arXiv200507709J}.
